A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-08-29 paper/paper.tex
art.cls, paper: MAJ
art.cls: MAJ
paper: better typesetting for iterated-param

\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape}
\usepackage[prefix=bonak]{art.cls/xkeymask}
\usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}

@@

% Some abbreviations
\newcommand{\imp}{\rightarrow}
\newcommand{\overright}[1]{\overrightarrow{#1}}
\renewcommand{\D}{D}
\newcommand{\hdD}{D.1}
\newcommand{\tlD}{D.2}
\renewcommand{\d}{d}
\renewcommand{\E}{E}
\newcommand{\ap}{\mathsf{ap}}
\renewcommand{\l}{l}
\renewcommand{\c}{c}
\newcommand{\pair}[2]{#1, #2}

% Fancy headers
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\footnotesize\textcolor{gray80}{{\thepage / \pageref{LastPage}}}}
\renewcommand{\sectionmark}[1]{\markboth{}{\thesection.\ #1}}
\fancyhead[L]{\footnotesize\textcolor{gray80}{{\MakeUppercase{\rightmark}}}}

% Section and subsection styles
\renewcommand{\thesection}{\Roman{section}}
\titleformat{\section}{\centering\scshape\Large\color{raspeberry}}{\thesection}{0.7em}{}
\titleformat{\subsection}{\strongenv\large\color{gray80}}{\thesubsection}{0.7em}{}

% Pack enumerate items and bibitems
\setlist{nolistsep}
\setlength{\bibitemsep}{.2\baselineskip plus .05\baselineskip minus .05\baselineskip}

@@

% Table caption set up
\DeclareCaptionFormat{hfillstart}{\hfill#1#2#3\par}
\DeclareCaptionFont{mdit}{\mdseries\itshape}
\captionsetup[table]{
  justification=centering,
  font=bf,
  labelfont=mdit,
}

% Fonts
\setmainfont{Avenir Next}
\setmonofont{Source Code Pro}
\defaultfontfeatures{Ligatures=TeX, Scale=MatchUppercase}

@@

where the filling conditions are conflated with the cube itself. $\Simplex{n}$ can be defined quite simply as the convex hull of $n$ points, but even defining the standard $n$-cube becomes a problem if we start with $\sq{n}$, but the situation becomes much more amenable if we define:

@@

\begin{align*}
  X_0 & : \U{}                                                                                                      \\
  X_1 & : X_0 \times X_0 \rightarrow \U{}                                                                           \\
  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \U{} \\
  \ldots
\end{align*}

@@

\subsection{Iterated parametricity}
A full 2-cube is made of two full 1-cubes connected by a lifted 1-cube made of two lines connecting the former points and a square connecting the former lines:
\begin{equation*}
  \begin{array}{lll}
    \mbox{\textit{squares}}     \\
    [1mm]\mbox{\textit{lines}}  \\
    [1mm]\mbox{\textit{points}} \\
    [1mm]\end{array}
  \framebox{$\begin{array}{lll}
        \framebox{$
            \begin{array}{ll}
               & \framebox{$a_{0\star}$}              \\
              \framebox{$a_{00}$}~\framebox{$a_{01}$} \\
            \end{array}
          $}~
        \framebox{$
            \begin{array}{ll}
               & \framebox{$a_{1\unitpoint}$}         \\
              \framebox{$a_{10}$}~\framebox{$a_{11}$} \\
            \end{array}
          $}~
        \raisebox{4.8mm}{$\framebox{$
                \begin{array}{ll}
                   & \framebox{$a_{\unitpoint\unitpoint}$}                    \\
                  \framebox{$a_{\unitpoint 0}$}~\framebox{$a_{\unitpoint 1}$} \\
                \end{array}
              $}$}
      \end{array}$}
\end{equation*}

>>>>

\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape}
\usepackage[prefix=bonak]{art.cls/xkeymask}

@@

% Some abbreviations
\newcommand{\imp}{\rightarrow}
\newcommand{\overright}[1]{\overrightarrow{#1}}
\renewcommand{\D}{D}
\newcommand{\hdD}{D.1}
\newcommand{\tlD}{D.2}
\renewcommand{\d}{d}
\renewcommand{\E}{E}
\newcommand{\ap}{\mathsf{ap}}
\renewcommand{\l}{l}
\renewcommand{\c}{c}
\newcommand{\pair}[2]{#1, #2}
\newcommandx{\myframe}[2][1,2]{\prim{frame}[][#1][#2][#2][]}
\newcommandx{\mylayer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\newcommandx{\myfiller}[2][1,2]{\prim{filler}[][#1][#2][][]}

@@

% Table caption set up
\DeclareCaptionFormat{hfillunittypet}{\hfill#1#2#3\par}
\DeclareCaptionFont{mdit}{\mdseries\itshape}
\captionsetup[table]{
  justification=centering,
  font=bf,
  labelfont=mdit,
}

@@

where the filling conditions are conflated with the cube itself. $\Simplex{n}$ can be defined quite simply as the convex hull of $n$ points, but even defining the standard $n$-cube becomes a problem if we unittypet with $\sq{n}$, but the situation becomes much more amenable if we define:

@@

\begin{align*}
  X_0 & : \U{}                                                                                                              \\
  X_1 & : X_0 \times X_0 \rightarrow \U{}                                                                                   \\
  X_2 & : \forall a b c d, X_1 (a, b) \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \rightarrow X_1 (c, d) \rightarrow \U{} \\
  \ldots
\end{align*}

@@

\subsection{Iterated parametricity}
A full 2-cube is made of two full 1-cubes connected by a lifted 1-cube made of two lines connecting the former points and a square connecting the former lines:
\begin{equation*}
  \begin{array}{l}
    \begin{array}{lll}
      \mbox{\textit{squares}}     \\
      [3mm]\mbox{\textit{lines}}  \\
      [3mm]\mbox{\textit{points}} \\
      [1mm]\end{array}
    \framebox{$\begin{array}{lll}
                     \overbrace{\raisebox{0.05cm}{\framebox{$
                           \begin{array}{ll}
                  \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[1][0]$}} & \framebox{$a_{0\unitpoint}$} \\
                  [1mm]\overbrace{\framebox{$a_{00}$}~\framebox{$a_{01}$}}   &
                  \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[1][0]\!\!\!\!\!\!\!\!$}}
                  \\
                \end{array}
                         $}}~
                     {\raisebox{0.05cm}{\framebox{$
                           \begin{array}{ll}
                  \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[1][0]$}} & \framebox{$a_{1\unitpoint}$} \\
                  [1mm]\overbrace{\framebox{$a_{10}$}~\framebox{$a_{11}$}}   &
                  \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[1][0]\!\!\!\!\!\!\!\!$}}
                \end{array}
                         $}}}}^{\mylayer[2][0]}~\stackrel{\raisebox{9.5mm}{$\framebox{$
                               \begin{array}{ll}
                      \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[2][1]$}}                   & \framebox{$a_{\unitpoint\unitpoint}$} \\
                      [1mm]\overbrace{\framebox{$a_{\unitpoint 0}$}~\framebox{$a_{\unitpoint 1}$}} &
                      \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[2][1]\!\!\!\!\!\!\!\!$}}
                    \end{array}$}$}}
                     {\raisebox{-0.4cm}{{\scriptsize \hspace{2.5cm}$\myfiller[2][0]\!\!\!\!\!\!\!$}}}
                   \end{array}$}
    ~~~\parbox{3.5cm}{{\it additionally, each atomic component at dimension $n$ is a $\myfiller[n][n]$}} \\
    [-1mm]\qquad\qquad~~
    \begin{tikzcd}
      \bullet\arrow[r, leftrightarrow] & \bullet\\
    \end{tikzcd}
    \mbox{\normalsize $\myframe[1][1]$}
    \quad~~
    \begin{tikzcd}
      \bullet\arrow[r, leftrightarrow] & \bullet \\
    \end{tikzcd}
    \mbox{\normalsize $\myframe[1][1]$}                                                                  \\
    [-2mm]\qquad\qquad
    \begin{tikzcd}
     \bullet\arrow[r, leftrightarrow] & \bullet\\
    \end{tikzcd}
    \mbox{\normalsize$\myframe[2][1]$}                                                                   \\
    [-2mm]\qquad\qquad
    \begin{tikzcd}
      \bullet\arrow[r, leftrightarrow] & \bullet\\
    \end{tikzcd}
    \mbox{\normalsize$\myframe[2][2]$}                                                                   \\
  \end{array}
\end{equation*}
